AggregateCounts

### 2021-09-20 R/AggregateCounts.Rmd
added figures for columns instead of scatter plots

@@

>>>>

PlotHistSumCols<- function(df, df2, fill){
ggplot()+
  geom_col(data = df,aes(x=as.factor(LogBin),y=NormalizedFrequency, fill = .data[[fill]]),
           size=3,position = position_dodge( width = .9))+
  geom_point(data = df2,
                aes(x=as.factor(LogBin),y=NormalizedFrequency, fill = .data[[fill]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1, shape = 1,show.legend = FALSE)+
  scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
  facet_grid(.~Species)+
  scale_fill_grey()+
  labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")))+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}

PlotHistSumCols(HistCondRegionSum%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint=="Day 4"),
                  HistReplicateSummary%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>%  
                    filter(TimePoint=="Day 4"), "Culture")#for mono vs co
PlotHistSumCols(HistCondRegionSum%>% filter(Culture == "co") %>% filter(TimePoint=="Day 4"),
                  HistReplicateSummary%>% filter(Culture == "co")%>%  filter(TimePoint=="Day 4"), "Strain")#for mono vs co

@@

#this is for the defense presentation
PlotAggsPlankcols<- function(df, df2, fill){
ggplot()+
  geom_col(data = df,aes(x=Aggregation,y=AgPlNormBiomass, fill = .data[[fill]]),
           size=3,position = position_dodge( width = .9))+
  geom_point(data = df2,
                aes(x=Aggregation,y=AgPlNormBiomass, fill = .data[[fill]]),
               position = position_jitterdodge(jitter.height = 0, jitter.width = .3,dodge.width = 0.75),size=1, shape = 1,show.legend = FALSE)+
  scale_y_continuous(limits = c(0,103),expand = expand_scale(mult = c(0, 0)))+
  facet_grid(.~Species)+
  scale_fill_grey()+
  labs(title = '', x = "", y = "Biomass contribution (%)")+
  theme_cowplot()+
  theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
        strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
        axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(margin = margin(1,0,0,0),size=13),
        axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}

PlotAggsPlankcols(plankAggHistCondReg%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint=="Day 4"),
                  plankAggHistRep%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>%  
                    filter(TimePoint=="Day 4"), "Culture")#for mono vs co
PlotAggsPlankcols(plankAggHistCondReg%>% filter(Culture == "co") %>% filter(TimePoint=="Day 4"),
                  plankAggHistRep%>% filter(Culture == "co")%>%  filter(TimePoint=="Day 4"), "Strain")#for mono vs co
